\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-06-26 tex/paper.tex
save

In many fields of science such as particle physics, climatology or population
genetics, computer simulators are used to describe complex processes that tie
parameters of an underlying theory to high dimensional observations. In most
cases, these implicit generative models~\citep{2016arXiv161003483M} are
specified as imperative implementations of forward stochastic processes that
generate data. Because it is usually computationally intractable, most simulators
do not provide a way to directly evaluate the likelihood function for a
given observation, thereby making inference difficult.

@@

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \}_{i=1}^N \sim p_r(\mathbf{x})$, simulator $g$.\\
        {\it Outputs:} proposal distribution $q(\theta|\psi)$, such that $p_r(\mathbf{x}) \approx p(\mathbf{x}|\psi)$.\\
        {\it Hyper-parameters:} The number $n_{\text{critic}}$ of training iterations of $d$; the size $M$ of a mini-batch; the gradient penalty coefficient $\lambda$; the entropy penalty coefficient $\gamma$.
    \end{flushleft}

@@

>>>>

In many fields of science such as particle physics, climatology or population
genetics, computer simulators are used to describe complex processes that tie
parameters of an underlying theory to high dimensional observations. In most
cases, these implicit generative models~\citep{2016arXiv161003483M} are
specified as procedural implementations of forward stochastic processes that
generate data. Because it is usually computationally intractable, most simulators
do not provide a way to directly evaluate the likelihood function for a
given observation, thereby making inference difficult.
In addition, most scientific simulators are written using opaque low-level programming
languages, hence raising raising the bar for likelihood-free inference
algorithms relying e.g. on the simulator being a function with computable derivatives~\citep{2016arXiv160507826G}
or being a controllable probabilistic program~\citep{2016arXiv161009900L}.

@@

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \sim p_r(\mathbf{x}) \}_{i=1}^N$, simulator $g$.\\
        {\it Outputs:} proposal distribution $q(\theta|\psi)$, such that $p_r(\mathbf{x}) \approx p(\mathbf{x}|\psi)$.\\
        {\it Hyper-parameters:} The number $n_{\text{critic}}$ of training iterations of $d$; the size $M$ of a mini-batch; the gradient penalty coefficient $\lambda$; the entropy penalty coefficient $\gamma$.
    \end{flushleft}

@@

\glnote{Compare with gradient-free optimization.}

\glnote{Wood -> assume that the simulator is probabilistic program.}
\glnote{Storkey -> assume access to derivatives.}
